General purpose gene annotation using deep learning

### 2020-01-09 paper/main.tex
paper figure

We also used multiple techniques to improve the prediction quality after the training was done. One very effective way was to input longer sequences during inference than during training. The sequences were up to 10 times larger, depending on species group and assembly quality. We also reconstructed the final predictions of a single model from overlapping predictions that were cut to a core sequence. This was done to drastically reduce a typical bias of the models towards the beginning and end of each sequence and also to provide the model with multiple different starting points. The different overlapping sequences were recombined by averaging the softmax values of each base. This was also done when we finally ensembled the whole output of different models on the softmax value level from (8?) different models. For more details on these post-processing techniques see Suplementary Material (?).

@@

\begin{figure}[!tpb]%figure1
\fboxsep=0pt\colorbox{gray}{\begin{minipage}[t]{235pt} \vbox to 100pt{\vfill\hbox to
235pt{\hfill\fontsize{24pt}{24pt}\selectfont FPO\hfill}\vfill}
\end{minipage}}
%\centerline{\includegraphics{fig01.eps}}
\caption{Caption, caption.}\label{fig:01}
\end{figure}

>>>>

	We also used multiple techniques to improve the prediction quality after the training was done. One very effective way was to input longer sequences during inference than during training. The sequences were up to 10 times larger, depending on species group and assembly quality. We also reconstructed the final predictions of a single model from overlapping predictions that were cut to a core sequence. This was done to drastically reduce a typical bias of the models towards the beginning and end of each sequence (see figure \ref{fig:length_wise_bias}) and also to provide the model with multiple different starting points. The different overlapping sequences were recombined by averaging the softmax values of each base. This was also done when we finally ensembled the whole output of different models on the softmax value level from (8?) different models. For more details on these post-processing techniques see Suplementary Material (?).

@@

\begin{figure}[!tpb]
	\centerline{\includegraphics[width=0.45\textwidth]{images/length_wise_bias}}
\caption{Caption, caption.}\label{fig:length_wise_bias}
\end{figure}
